### 2013-09-30 tex/scam/appendix.tex
typos

Suppose for all $j,k$, $\lambda_n > | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|$, then $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}.

@@

\begin{align*}
\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( \hat{r}_k - \Delta_k \hat{d}_k + \hat{c}_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \hat{r}_k - \Delta_k d_k + c_k \mathbf{1}) + \gamma_k
\end{align*}
In the derivatives, $\mathbf{u}$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.

We now substitute in $\hat{d}_k = 0, \hat{c}_k=0$ and show that the duals can be set in a way to ensure that the derivatives are equal to 0.

>>>>

Suppose for all $j=1,...,n, k\in S^c$, $\lambda_n > | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|$, then $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}.

@@

\begin{align*}
\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( r_k - \Delta_k \d_k 
       + \c_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \r_k - \Delta_k \d_k 
       + \c_k \mathbf{1}) + \gamma_k
\end{align*}
In the derivatives, $\mathbf{u}$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.

We now substitute in $d_k = \hat{d}_k = 0, c_k=\hat{c}_k=0, r_k = \hat{r}_k = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to 0.
